---
title: "Assignment 5"
author: "Bridget Brady"
date: "October 11, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)

```


```{r}
library(tidyr)
```


```{r}
library(dplyr)
tallestbuildings=read.csv("tallestbuildings.csv")
```

Display how many buildings are there in each city represented in that dataset

```{r}
tallestbuildings$City=as.character(tallestbuildings$City)
tallestbuildings$City=gsub("ÿ","",tallestbuildings$City)
head(tallestbuildings$City)
```



```{r}
tallestbuildings %>%group_by(City)%>%tally()%>%ggplot(.,aes(reorder(City,n),n))+geom_bar(stat="identity")+coord_flip() 


```

Mean Height as a Graph by City

```{r}
tallestbuildings$Height..ft.=as.character(tallestbuildings$Height..ft.)
tallestbuildings$Height..ft.=gsub(",","",tallestbuildings$Height..ft.)
tallestbuildings$Height..ft.=as.numeric(tallestbuildings$Height..ft.)

tallestbuildings %>% group_by(City) %>%  summarise(Mean.Height=round(mean(Height..ft.,na.rm=TRUE),2))%>%
    ggplot(aes(x=reorder(City,Mean.Height), y=Mean.Height)) +
    geom_bar(stat="identity")+xlab("")+coord_flip()
```

Installed Countrycode

```{r}
#install.packages("countrycode")
library(countrycode)
```


Separated Cities and Countries

```{r}
newtallestbuildings=tallestbuildings %>% separate(City,c("City","Country"), sep="[:punct:]")
```

Display how many buildings are there in each Country represented in that dataset

```{r}
newtallestbuildings %>%group_by(Country)%>%tally()%>%ggplot(.,aes(reorder(Country,n),n))+geom_bar(stat="identity")+coord_flip() 
```

Mean Height as a Graph by Country

```{r}
newtallestbuildings$Height..ft.=as.character(newtallestbuildings$Height..ft.)
newtallestbuildings$Height..ft.=gsub(",","",newtallestbuildings$Height..ft.)
newtallestbuildings$Height..ft.=as.numeric(newtallestbuildings$Height..ft.)

newtallestbuildings %>% group_by(Country) %>%  summarise(Mean.Height=round(mean(Height..ft.,na.rm=TRUE),2))%>%
    ggplot(aes(x=reorder(Country,Mean.Height), y=Mean.Height)) +
    geom_bar(stat="identity")+xlab("")+coord_flip()
```


Color Added

```{r}
newtallestbuildings %>% group_by(Country) %>%  summarise(Mean.Height=round(mean(Height..ft.,na.rm=TRUE),2))%>%
    ggplot(aes(color=Country, fill=Country, x=reorder(Country,Mean.Height), y=Mean.Height)) +
    geom_bar(stat="identity")+xlab("")+coord_flip() 
```


Mean heights (in feet) of buildings that are used for different purposes

```{r}
tallestbuildings %>% group_by(Use) %>%  summarise(Mean.Height=round(mean(Height..ft.,na.rm=TRUE),2))%>%
    ggplot(aes(x=reorder(Use,Mean.Height), y=Mean.Height)) +
    geom_bar(stat="identity")+xlab("")+coord_flip()
```


Mean heights (in feet) of buildings that are used for different purposes in color

```{r}
tallestbuildings %>% group_by(Use) %>%  summarise(Mean.Height=round(mean(Height..ft.,na.rm=TRUE),2))%>%
    ggplot(aes(color=Use, fill=Use, x=reorder(Use,Mean.Height), y=Mean.Height)) +
    geom_bar(stat="identity")+xlab("")+coord_flip()
```


